### 2019-05-30 doc/chapters/trying_verify_checktx.tex
added image
added comment image
fixed typo
chapter description

\chapter{Trying to Verify checkTransaction}
\label{chap:connecting}
// TODO

@@

We arrive at the decision that we need a smaller part to verify.
We have chosen to verify the addition with zero of Bitcoin-Ss CurrencyUnit class as described in the next chapter.

@@

Here, Bitcoin-S did a bit too much and marked all transaction as invalid, if they referenced a transaction twice in the next transaction.
The fix is, to check on TransactionOutPoint instead of TransactionOutPoint.txId, because TransactionOutPoint contains the txId as well as the output index it references.
\begin{lstlisting}[language=scala]
  val prevOutputs = transaction.inputs.map(_.previousOutput)
  val noDuplicateInputs = prevOutputs.distinct.size == prevOutputs.size
\end{lstlisting}
Since TransactionOutPoint is a case class and Scala has a built in == for case classes there is no need to implement TransactionOutPoint.==.

@@

>>>>

\chapter{Trying to Verify checkTransaction}
\label{chap:connecting}

This chapter describes some parts of Bitcoin-S.
We are going to create a transaction and show you the relevant parts of checkTransaction, where transactions are checked against some properties.
Then we see some troubles occurred during this work.
In the end you will see how we fixed a bug in Bitcoin-S.

@@

We arrived at the decision that we need a smaller part to verify.
We have chosen to verify the addition with zero of Bitcoin-Ss CurrencyUnit class as described in the next chapter.

@@

Here, Bitcoin-S did a bit too much and marked all transaction as invalid, if they referenced a transaction twice in the next transaction.
The fix is, to check on TransactionOutPoint instead of TransactionOutPoint.txId, because TransactionOutPoint contains the txId as well as the output index it references.
\begin{lstlisting}[language=scala]
  val prevOutputs = transaction.inputs.map(_.previousOutput)
  val noDuplicateInputs = prevOutputs.distinct.size == prevOutputs.size
\end{lstlisting}
Since TransactionOutPoint is a case class and Scala has a built in == for case classes there is no need to implement TransactionOutPoint.==.
\begin{figure}[H]
	\centering
		\includegraphics[scale=0.396]{images/bitcoin-s-pr.png}
	\caption{Line changes for PR \#435 from GitHub}
	\label{fig:output1}
\end{figure}

@@

\begin{figure}[H]
	\centering
		\includegraphics[scale=0.5]{images/bitcoin-s-pr-comment.png}
	\caption{Nice catch comment on PR \#435 from GitHub}
	\label{fig:output1}
\end{figure}
